\documentclass[letter,10pt]{article}
\usepackage{TLCresume}
\begin{document}

\subsection{{Fullstack Web3 Developer \hfill JUL 2024 --- PRESENT}}
\subtext{RapidNode \hfill Remote, India}
\begin{zitemize}
  \item Architected and scaled high-throughput AI data pipelines, reducing processing latency by 40\% through optimized vector search and caching layers (PGVector/Redis).
  \item Engineered autonomous AI agents, implementing robust error handling and monitoring using Prometheus/Grafana to maintain 99.9\% service uptime.
  \item Scaled backend services using Go and NestJS to handle 10k+ concurrent requests, ensuring system stability under high load.
  \item Designed and maintained asynchronous message-driven architecture using RabbitMQ for reliable cross-service communication.
  \item Built enterprise One View dashboard for investment firms tracking Discord, Twitter, and Telegram ecosystems.
  \item Developed Go-based monitoring service handling 10,000+ nodes with Prometheus integration.
  \item \textbf{Tech}: Go, Python, PostgreSQL, NestJS, TypeScript, RabbitMQ, Prometheus, Grafana
\end{zitemize}

\subsection{{Fullstack Developer (Part-time) \hfill MAY 2025 --- PRESENT}}
\subtext{Syntax Studios \hfill Remote}
\begin{zitemize}
  \item Led development of complex enterprise-grade dashboards, focusing on real-time data visualization and performant state management.
  \item Integrated LLM-based workflows into existing product suites, improving automation capabilities for end-users.
  \item Optimized frontend-to-backend data flow, significantly reducing payload sizes and improving overall application responsiveness.
  \item \textbf{Tech}: React, Next.js, Node.js, TailwindCSS, Privy, Solidity, MongoDB
\end{zitemize}

\subsection{{ Fullstack Blockchain Developer \hfill JUN 2023 --- JUN 2024}}
\subtext{Clamp \hfill Mumbai, India}
\begin{zitemize}
  \item Developed core foundational services for cross-chain financial infrastructure, focusing on high-integrity data processing and transaction management.
  \item Implemented automated CI/CD pipelines, streamlining deployment cycles and reducing production bugs by 60\%.
  \item Collaborated on the architecture of distributed systems, ensuring data consistency across multiple database instances.
  \item \textbf{Tech}: Solidity, Next.js, Node.js, TypeScript, MongoDB, React Native
\end{zitemize}

\end{document}