\documentclass[letter,10pt]{article}
\usepackage{TLCresume}
\begin{document}

\subsection{{AI \& Web3 Developer (Contract) \hfill NOV 2025 --- JAN 2026}}
\subtext{DeFi Protocol (NDA) \hfill Remote, USA}
\begin{zitemize}
  \item Co-engineered an \textbf{EIP-7540 async vault} in \textbf{Solidity} deployed on \textbf{Arbitrum}, enabling permissioned execution for both human and AI agents via the \textbf{MetaMask Delegation Toolkit}; designed the core liquidity tracking model for deployed and undeployed vault positions adopted in the final implementation.
  \item Authored a \textbf{custom GMX \texttt{createOrder} calldata generation script} to bypass a buggy internal on-chain-actions product, combining raw calldata construction with the \textbf{GMX SDK} and \textbf{MetaMask delegation signatures} to enable permissioned vault trade execution.
  \item Built a \textbf{GMX x Allora AI trading agent} in \textbf{TypeScript} and \textbf{LangGraph} as a standalone backend proof-of-concept executing real-time long and short positions on \textbf{Arbitrum} driven by \textbf{Allora network} price predictions.
  \item Validated trading flows on a \textbf{Tenderly mainnet fork} achieving zero transaction reverts; delivered the full prototype within \textbf{2 weeks} while learning \textbf{LangGraph} from scratch.
  \item Developed an \textbf{agentic hire/fire control interface} via \textbf{CopilotKit}, allowing users to spawn, manage, and terminate trading agents through natural language with on-chain settlement.
  \item \textbf{Tech}: Solidity, TypeScript, LangGraph, GMX SDK, MetaMask Delegation Toolkit, CopilotKit, Tenderly, Arbitrum
\end{zitemize}

\subsection{{Web3 Solutions Engineer \hfill JAN 2025 --- NOV 2025}}
\subtext{BuildBear Labs \hfill Remote, Singapore}
\begin{zitemize}
  \item Created end-to-end \textbf{Web3 CI/CD test flows} with BuildBear, showcasing integrations and testing with complex protocols like \textbf{Uniswap V4} and V3, covering setup, whitelisting, automated deployment, and testing with GitHub Actions.
  \item Spearheaded onboarding for \textbf{Across} and \textbf{LI.FI} bridge protocol teams, architecting testing solutions that yielded \textbf{50+ plugin access requests each} within 30 days of launch.
  \item Performed black-box testing of pre-release features, identifying edge-case failures and providing technical feedback across product, frontend, backend, and infrastructure teams.
  \item Researched and produced in-depth \textbf{video walkthroughs} and written tutorials for Across, LI.FI, and Pimlico paymaster plugins on BuildBear Sandbox environments.
  \item \textbf{Tech}: Solidity, Foundry, TypeScript, Node.js, GitHub Actions, BuildBear SDK
\end{zitemize}


\subsection{{Smart Contract Auditor Intern \hfill SEPT 2024 --- DEC 2024}}
\subtext{Nethermind \hfill Remote, United Kingdom}
\begin{zitemize}
  \item Conducted security reviews across \textbf{re-staking} protocols, \textbf{AA paymasters}, \textbf{bridges}, \textbf{governance} modules, and \textbf{proof-of-liquidity} mechanisms.
  \item Reported vulnerabilities and provided mitigations to enhance smart contract security across \textbf{Solidity} and \textbf{Cairo} ecosystems.
\end{zitemize}


\subsection{{Full Stack Web2 \& Web3 Intern \hfill APRIL 2024 --- JULY 2024}}
\subtext{Kyte Social \hfill Remote, India}
\begin{zitemize}
  \item Developed smart contracts with \textbf{Solidity} implementing \textbf{ERC721} and \textbf{ERC1155} NFT standards using \textbf{OpenZeppelin}; tested with \textbf{Foundry} unit, fuzz, and invariant tests.
  \item Integrated smart contracts with frontend using \textbf{NextJS}, \textbf{Wagmi}, \textbf{Viem}, \textbf{EthersJS}, and \textbf{Web3JS}.
  \item Developed a form enabling rapid NFT collection creation, \textbf{reducing user time and effort by 90\%} while abstracting underlying complexities.
  \item Synced on-chain data to \textbf{MongoDB} backend; signed off-chain messages for reward claiming via \textbf{NodeJS} server using \textbf{Web3JS}.
  \item \textbf{Tech}: Solidity, Foundry, Next.js, Wagmi, Viem, MongoDB, Node.js
\end{zitemize}

\end{document}
