\section{{\color{MidnightBlue}{Projects}}}
\vspace{-10pt}
\resumeSubHeadingListStart

% --- Tessera RAG Platform ---
\resumeProjectHeading
{\textbf{Tessera} $|$ {\color{blue}\href[pdfnewwindow=true]{https://tessera-rag-ai.vercel.app}{\underline{Live Demo}}} $|$ {\color{blue}\href[pdfnewwindow=true]{https://github.com/JustUzair/Tessera-RAG-AI}{\underline{Github}}} $|$ {\color{blue}\href[pdfnewwindow=true]{https://documenter.getpostman.com/view/20867739/2sBXihrYt8}{\underline{API Docs}}}}
\vspace{-5pt}
\resumeItemListStart
\resumeItem{\textit{\textbf{Next.js 16}, \textbf{Express}, \textbf{MongoDB Atlas}, \textbf{LangChain}, \textbf{Vector Search}, \textbf{Zod}, \textbf{Framer Motion}, \textbf{Spline}}}
\resumeItem{Built a \textbf{production RAG platform} where users upload documents, ask questions, and receive \textbf{citation-backed answers with zero hallucination}. Every response includes clickable source chunks proving where the answer originated.}
\resumeItem{Architected \textbf{constraint-based agent design}: LangChain agent forbidden from answering until invoking \texttt{kb\_search} tool. \textbf{Structured JSON via Zod} prevents model responses from violating schema. Eliminates hallucination at the system level, not prompt engineering.}
\resumeItem{Engineered \textbf{semantic embedding cache} via CacheBackedEmbeddings to MongoDB KV store: document re-upload drops from \textbf{2.31s to 421ms} (82\% reduction). Namespace-based deduplication eliminates wasted embedding API calls.}
\resumeItem{Frontend: 3D Spline hero, Framer Motion animations, drag-and-drop KB panel, conversation threading, paginated history, full dark mode. \textbf{Lighthouse: Performance 92, Accessibility 96, Best Practices 100, SEO 100}.}
\resumeItem{Deployed on Vercel with Postman API docs and Vitest test suite validating ingestion, querying, schema enforcement, and citation integrity.}
\resumeItemListEnd

\vspace{-10pt}

% --- AXIOM ---
\resumeProjectHeading
{\textbf{AXIOM} $|$ {\color{blue}\href[pdfnewwindow=true]{https://axiom-ai-justuzair.vercel.app}{\underline{Live Demo}}} $|$ {\color{blue}\href[pdfnewwindow=true]{https://axiom-lcel-backend-justuzair.vercel.app}{\underline{Backend}}} $|$ {\color{blue}\href[pdfnewwindow=true]{https://documenter.getpostman.com/view/20867739/2sBXcLgHZF}{\underline{API Docs}}} $|$ {\color{blue}\href[pdfnewwindow=true]{https://github.com/JustUzair/axiom-lcel-rag}{\underline{Github}}}}
\vspace{-5pt}
\resumeItemListStart
\resumeItem{\textit{\textbf{TypeScript}, \textbf{Next.js}, \textbf{Express}, \textbf{LangChain LCEL}, \textbf{LightRAG}, \textbf{Tavily}, \textbf{Spline}, \textbf{Vercel Serverless Functions}}}
\resumeItem{Engineered a dual-mode AI search engine with a deterministic router using \textbf{30+ regex patterns} across 8 intent categories (pricing, recency, comparisons, URLs, reviews, etc.) to eliminate unnecessary LLM calls.}
\resumeItem{Web pipeline scrapes and summarizes the \textbf{top 5 results} in parallel, with graceful snippet fallback; KB pipeline chunks documents with a \textbf{200-char overlap window}, embedded as \textbf{Light-RAG}, and returns confidence-scored answers with full source citations.}
\resumeItem{Covered both pipelines with a \textbf{Vitest} integration test suite validating ingestion, querying, \textbf{Zod} schema enforcement (400s on bad input), and citation integrity; deployed rate-limited \textbf{Express} backend on \textbf{Vercel Serverless}.}
\resumeItem{Built a polished \textbf{Next.js} frontend featuring a \textbf{Spline 3D} hero, mouse-tracked spotlight, ambient orb backgrounds, per-word answer streaming reveals, and scramble-on-mount text animations via \textbf{Framer Motion}.}
\resumeItemListEnd

\vspace{-10pt}
% --- Mintrrs ---
\resumeProjectHeading
{\textbf{Mintrrs} $|$ {\color{blue}\href[pdfnewwindow=true]{https://github.com/JustUzair/NFT-Generator}{\underline{Github}}} $|$ {\color{blue}\href[pdfnewwindow=true]{https://www.postman.com/justuzair/workspace/justuzair-ughsal-nft-gen-nextjs}{\underline{API Docs}}}}
\vspace{-5pt}
\resumeItemListStart
\resumeItem{\textit{\textbf{Next.js}, \textbf{TypeScript}, \textbf{Tailwind}, \textbf{Solidity}, \textbf{Foundry}, \textbf{Wagmi}, \textbf{Viem}, \textbf{IPFS}, \textbf{MongoDB}}}
\resumeItem{Designed and deployed a \textbf{Factory Pattern} smart contract system, \texttt{NFTCollectionFactory} deploys isolated \textbf{ERC1155} collection contracts per artist, with \textbf{OpenZeppelin} Pausable, Supply, and Ownable extensions; tested end-to-end with a \textbf{Foundry} test suite and Forge deploy scripts.}
\resumeItem{Implemented dual-payment minting in Solidity accepting \textbf{native ETH} or \textbf{ERC20 (USDC)} via \texttt{transferFrom}, with per-address holder dedup via nested mappings, \textbf{batch minting}, and an \textbf{owner revenue withdrawal} function.}
\resumeItem{Serverless \textbf{Next.js} API routes handle SVG layer combination, \textbf{hash-map-based} duplicate prevention, and algorithmic generation; automated \textbf{IPFS} pipeline via \textbf{Pinata} pins images and metadata as a directory with the collection URI written on-chain post-deploy.}
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-10pt}